---
title: "Lecture 7_8ab"
author: "Jiansong Xu"
date: "February 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 7 

(a)
```{r}
BW <- read.csv("U:/stat475/assignment2/placekick.BW.csv")
BW.fit <- glm(Good ~ Distance + Weather + Wind15 + Temperature + Grass + Pressure + Ice,family = binomial(link = logit), data = BW)
summary(BW.fit)
```
Indicator variables: 
Good represents the success of the kick, Y for success, N for failure; 

Wind15 indicates the wind level, 1 for >15, 0 otherwise; 

Grass represents if the field is grass field, 1 for grass, 0 otherwise;

Pressure indicates the time left before the game ends, Y for less than 3 minutes, N otherwise.

Temperature gives 3 levels of temperature measures. 

Weather indicates the weather condition during game place, containing 4 levels.

(b)
We can use relevel() function to re-indicate the level of each level of Weather, such that we specify the level of "sun" to 0.
