---
title: "Assignment 1"
author: "Jiansong Xu"
date: "January 18, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(binom)
library(dplyr)
```
#Lecture 3

1. 

a.
1)	There are n identical trails. This is satisfied, since each observation was recorded at the same town, same intersection, within one-half an hour time range. 

2)	There are 2 possible outcomes. This is satisfied, because the car is either alternative fuel using or not. 

3)	Each trail is independent to others. This condition is satisfied, because the type of one car does not affect the type of next car being observed.  

4)	The possibility of success remains constant through trails.  This condition holds, because this is not likely to be affected by excluded measures.

5)	The random variable of interest W is number of success. Satisfied, in this experiment , W=14.

b. 
```{r}
alpha <- 0.05
w <- 14
n <- 125
pi.hat <- w/n
var.pi.hat <- pi.hat*(1-pi.hat)/n
pi.0 = 0.08
```

```{r}
chop <- c("agresti-coull", "asymptotic", "wilson", "exact")
binom.confint(x = w, n = n, conf.level = 1-alpha, methods = "all") %>% filter(method %in% chop) -> CI1
CI1
```

c. 
#Use 2-side Likelihood Ration test H0: pi = 0.08 Ha: pi != 0.08
```{r}
LR <- -2*(w*log(pi.0/pi.hat) + (n-w)*log((1-pi.0)/(1-pi.hat)))
p.LR2 <- 1 - pchisq(LR, df=1) #2-side p value
list(LR=LR, P = p.LR2)
```

We fail to reject H0, so we cannot conclude the probability in this intersection is differ from nationwide probability.

2.
```{r}
alpha <- 0.05
w2 <- 79
n2 <- 80
pi.hat2 <- w2/n2
var.pi.hat2 <- pi.hat2*(1-pi.hat2)/n
pi2.0 = 1
```

```{r}
chop2 <- c("asymptotic", "wilson")
binom.confint(x = w2, n = n2, conf.level = 1-alpha, methods = "all") %>% filter(method %in% chop2) -> CI2
CI2
```

(a) Wald CI: [0.963 - 1.011]. We except 95% of similarly constructed intervals to contain the true probability of a random selected resident to oppose the tax.

(b) Wilson CI: [0.033 - 0.998]. We expect 95% of similarly constructed intervals to contain the parameter pi which represents the true probability of a random selected resident to oppose the tax.

(3) We can testify this by performing Score test. H0: pi = 1, Ha: pi < 1
```{r}
# Score Test Manual
(Z0 = (pi.hat2 - pi2.0)/sqrt(0.5*0.5/n2))
(p.score <- pnorm(Z0)) #lower tail p-value
```
Base on p value we fail to reject H0, so it is possible for pi = 1.

(d)
I prefer the Wilson CI, as it is constructed using the pi corresponding to the null hypothesis, and the sample size is rather small, so Wilson performs better.


3.
```{r}
n3 = 1000 #large sample
n3.1 = 10 #small sample
```

(a)
```{r}
binom.confint()
```








#Lecture 4

1.
```{r}
library(PropCIs)
alpha <- 0.05

#No time-out group
w.v <- 22
n.v <- 26 
#Time-out group
w.p <- 10
n.p <- 16 
```

(a)
```{r}
wald2ci(x1=w.v, n1=n.v, x2=w.p, n2=n.p, conf.level = 0.95, adjust = "Wald")
```

```{r}
wald2ci(x1=w.v, n1=n.v, x2=w.p, n2=n.p, conf.level = 0.95, adjust = "AC")
```

```{r}
diffscoreci(x1=w.v, n1=n.v, x2=w.p, n2=n.p, conf.level = 0.95)
```
For each type of interval: we expect 95% of all similarly constructed intervals to contain the true value of the difference between the probabilities of success of 2 strategy groups.

(b)
```{r}
#score
prop.test(x=c(w.v, w.p), n=c(n.v, n.p), alternative="less", correct=FALSE)
```
Based on large p value, we fail to reject H0: pi1 = pi2.
```{r}
#LR
kicmat <- matrix(data=c(w.v, w.p, n.v-w.v, n.p-w.p), nrow=2)
library(vcd)
assocstats(kicmat)
```
We cannot reject H0 using LR test, as p value is greater than alpha = 0.05.

2.
```{r}
#Non-native group
w.v2 <- 118
n.v2 <- 211

#Native group
w.p2 <- 155
n.p2 <- 206
```

H0: pi1 - pi2 = 0  
Ha: pi1 - pi1 < 1
alpha = 0.05

Use score test
```{r}
prop.test(x=c(w.v2, w.p2), n=c(n.v2, n.p2), alternative="less", correct=FALSE)
```
We reject H0 because p value is smaller than alpha.
So we conclude that non-native English speaking students do not pick up on humor as much as native English speaking stduents.  






