---
title: "Lec25_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(dplyr)
challenger <- read.csv("challenger.csv")
```

(a)
```{r}
## Fit a logistic regression model
## Aggregate data
w <- aggregate(O.ring ~ Temp, FUN = sum, data = challenger)
n <- aggregate(O.ring ~ Temp +Number, FUN = length, data = challenger) 

#Each row has 6 obs, so multiply each length by 6 to get number of Trials.
n %>% mutate(Trials = Number*O.ring) %>% select(-Number, -O.ring) -> n 

# Output data
aggdat <- data.frame(O.ring = w$O.ring, Temp = w$Temp, Trials = n$Trials)
aggdat %>% mutate(Proportion = round(O.ring/Trials, 2)) -> aggdat

## Use summary() to examine residual deviance and df
lfit <- glm(O.ring/Trials ~ Temp, weights = Trials, family = binomial(link = "logit"), data = aggdat)
(lsum <- summary(lfit))
rdev <- lfit$deviance 
dfr <- lfit$df.residual 

# Deviance/df statistic
ddf <- rdev/dfr 
thresh2 <- 1 + 2*sqrt(2/dfr) 
thresh3 <- 1 + 3*sqrt(2/dfr) 
round(c(rdev, dfr, ddf, thresh2, thresh3), digits=2)
```
```{r}
## Graphic assessment of residuals
s.res <- rstandard(lfit, type = "pearson")
grp <- round(data.frame(aggdat, s.res), 2)
plot(x=grp$Temp, y=grp$s.res, xlab = "Tempurature", ylab = "Standerdized Pearson residual", main = "Standerdized Pearson residuals vs. /n x")
abline(h = c(3, 2, 0, -2, -3), lty = "dotted", col = "blue")
```

From the D/df we see the ratio isn't even close to the first threshold, base on this rough test the model fit seems good. Yet from the graph we see an extreme residual. 




(b)
```{r}
## LR test
c(rdev, dfr, pchisq(q=rdev, df=dfr, lower.tail=FALSE))
```
LR Goodness-of-fit test:


H0: the model is a good fit;  Ha: model is not a good fit.

p-value = 0.06

We failed to reject H0, thus we do not have enough evidence to suggest that this model is a poor fit.



```{r}
## Examine expected counts
pi.hat <- predict(lfit, type = "response") 
p.res <- residuals(lfit, type = "pearson") 
pear <- sum(p.res^2)
aggdat$pi.hat <- pi.hat
aggdat$p.res <- p.res
aggdat$exp.succ <- aggdat$Trials * aggdat$pi.hat
aggdat$exp.fail <- aggdat$Trials * (1 - aggdat$pi.hat)
round(aggdat[,c("Temp", "Trials", "pi.hat", "exp.succ", "exp.fail")], digits=2) -> exps
summary(exps[,4:5])
```
The expected success is really low that even the maximum is merely 1.56, so the LR is not valid in this case.