---
title: "lec10_4"
author: "Jiansong Xu"
date: "February 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##4

_Test for effect of field_
perform a LR test on each variable
For field: H0: beta_2 = 0, Ha:beta_2 != 0
```{r}
library(car)
placekick <- read.csv("Placekick.csv")
typeof(placekick$field)
placekick <- transform(placekick, field = as.factor(field))
mod.fit <- glm(good ~ distance + field, family = binomial(link = "logit"), data = placekick)
Anova(mod.fit, test = "LR")
```
For the output we see the variable "field" is not significant for model fit. So we conclude there is no effect on probability of success due to type of field. 

_At different distances_
```{r}
beta.hat <- coef(mod.fit)[-1]
all.dist <- seq(from = 20, to = 60, by = 10)
OR.field <- exp(beta.hat[1]*all.dist + beta.hat[2])
round(cbind(all.dist, OR.field), digits=2)
```
The effect of field at different distances varies. At distance 20 the effect appears to be the strongest, then diminishes when distance gets larger and larger.