---
title: "lec11_q2"
author: "Jiansong Xu"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Ex2
(a)
```{r}
tomato <- read.csv("TomatoVirus.csv")
tomato <- transform(tomato, Infest = as.factor(Infest))
mod.fit<-glm(formula = Virus8/Plants ~ Infest + Control, family = binomial(link = logit), data = tomato,
    weights = Plants)
##Set baseline to N since we are comparing to no-control group. 
tomato$Control <- relevel(tomato$Control, ref = "N")
#exponentiate coefficient of controlC to get the OR of controlC to controlN
exp(mod.fit$coefficients[3])
# Profile likelihood ratio interval
exp(confint(object = mod.fit, parm = "ControlC", level = 0.95))
```
The odds of being affected with chemical control is 0.45 times as high as with no control.
We expect 95% of all similarily constructed [0.35, 0.58] intervals to contain the odds ratio of being affected of controlC to controlN.

(b)
Do a significance test on the interaction term Infest2:ControlC.
H0: beta_6 = 0(interaction of Infest2 and ControlC has no effect in the model)
Ha: beta_6 != 0
```{r}
library(car)
mod.fit.inter <- glm(formula=Virus8/Plants ~ Infest + Control + Infest:Control, family=binomial(link=logit), data=tomato, weights=Plants)
summary(mod.fit.inter)
```
Infest2:ControlC is not significant under alpha = 0.05, so we do not reject H0, thus we can conclude that changing infest type doesn't have impact on the performance of chemical control method. 