---
title: "Lec13_1"
author: "Jiansong Xu"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1

(a)
```{r}
shuttle <- read.csv("challenger.csv")
probit.fit <- glm(O.ring/Number ~ Temp, family = binomial(link = "probit"), weights = Number, data = shuttle)
summary(probit.fit)
```
(b)
```{r}
log.fit <- glm(O.ring/Number ~ Temp, family = binomial(link = "cloglog"), weights = Number, data = shuttle)
summary(log.fit)
```
(c)
```{r}
fit <- glm(O.ring/Number ~ Temp, family = binomial(link = "logit"), weights = Number, data = shuttle)
curve(expr = predict(object = probit.fit, newdata = data.frame(Temp = x), type = "response"), col = "red", xlim = c(30, 90))
curve(expr = predict(object = log.fit, newdata = data.frame(Temp = x), type = "response"), col = "blue", xlim = c(30, 90), add = TRUE)
curve(expr = predict(object = fit, newdata = data.frame(Temp = x), type = "response"), col = "black", xlim = c(30, 90), add = TRUE)
```

(d)
```{r}
alpha = 0.05
##Probit
probit.pred <- predict(probit.fit, newdata = data.frame(Temp = 31), type = "response", se = TRUE)
probit.pred$fit
CI.pro.lower <- probit.pred$fit - qnorm(p=c(1 - alpha/2))*probit.pred$se
CI.pro.upper <- probit.pred$fit + qnorm(p=c(1 - alpha/2))*probit.pred$se
CI.pro <- cbind(CI.pro.lower, CI.pro.upper)
CI.pro
```
The predicted failure rate when temp = 31 is 0.696.
We expected 95% of all similarly constructed intervals that are [0.109, 1.284] to contain the probability of failure when Temp = 31.

```{r}
##cloglog
log.pred <- predict(log.fit, data.frame(Temp = 31), type = "response", se = TRUE)
ci.log.lower <- log.pred$fit - qnorm(p=c(1-alpha/2))*log.pred$se
ci.log.upper <- log.pred$fit + qnorm(p=c(1-alpha/2))*log.pred$se
ci.log <- cbind(ci.log.lower, ci.log.upper)
log.pred$fit
ci.log
```
The predicted failure rate when temp = 31 is 0.973.
We expected 95% of all similarly constructed intervals that are [0.692, 1.254] to contain the probability of failure when Temp = 31.

```{r}
##Logistic
pred <- predict(fit, data.frame(Temp = 31), type = "response", se = TRUE)
lower<- pred$fit - qnorm(p=c(1-alpha/2))*pred$se
upper <- pred$fit + qnorm(p=c(1-alpha/2))*pred$se
ci <- cbind(lower, upper)
pred$fit
ci
```
The predicted failure rate when temp = 31 is 0.818.
We expected 95% of all similarly constructed intervals that are [0.346, 1.289] to contain the probability of failure when Temp = 31.

(e)
```{r, messsage = FALSE}
library(dplyr)
rbind(CI.pro, ci.log, ci) %>% cbind(rbind(probit.pred$fit, log.pred$fit, pred$fit)) -> compare
rownames(compare) <- c("probit", "cloglog", "logistic")
colnames(compare)[3] <- "predict"
compare
```
CIs are not similar, as the logistic model prediction has a wider CI, and probit gives a quite narrow CI.
And predictied failure rates are not similar among methods. 