---
title: "lec14_1"
author: "Jiansong Xu"
date: "March 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1
(a)
```{r}
pearson <- function(counts){chisq.test(x=counts, p=c(9,3,3,1)/16, correct=FALSE)$statistic}

samp.size <- 1611
set.seed(123)
rcount <- rmultinom(n=1000, size=samp.size, prob=c(9,3,3,1)/16)
p.stats <- apply(X=rcount, MARGIN=2, FUN=pearson)
summary(p.stats)
hist(x=p.stats, breaks=c(0:50)/2, freq=FALSE, main="Histogram of Pearson Stats for Simulated Data")
curve(expr=dchisq(x=x, df=3), add=TRUE, col="red")

# Add line at the 0.05 critical value of chi-squared(3)
abline(v=qchisq(0.95, df=3), col="blue")
```
Chi-square seems like a good fit.

(b)
i
```{r}
n <- 10
probs <- c(9,3,3,1)/16
n*probs -> counts10
list10 <- as.list(counts10)
names(list10) <- c("Tall cut-Leaf", "Tall potato-leaf", "Dwarf cut-leaf", "Dwarf potato-leaf")
data.frame(list10)
```
ii
```{r, warning=FALSE}
samp.size <- 10
set.seed(123)
rcount <- rmultinom(n=1000, size=samp.size, prob=c(9,3,3,1)/16)
p.stats <- apply(X=rcount, MARGIN=2, FUN=pearson)
hist(x=p.stats, breaks=c(0:50)/2, freq=FALSE, main="Histogram of Pearson Stats for Simulated Data")
invisible(curve(expr=dchisq(x=x, df=3), add=TRUE, col="red"))
# Add line at the 0.05 critical value of chi-squared(3)
abline(v=qchisq(0.95, df=3), col="blue")
```

The curve dose not fit histogram very well, although there is a slightly observable Chi-square shape. The right-tail has been stretched very long, because a larger portion of statistics are far away beyond the critical value comparing to the large sample size we had in the last part. 

(c)
```{r}
##Make a function which draws graphs for later use
probs <- c(9,3,3,1)/16

draw <- function(ss) {
  
n <- ss
n*probs -> counts
list <- as.list(counts)
names(list) <- c("Tall cut-Leaf", "Tall potato-leaf", "Dwarf cut-leaf", "Dwarf potato-leaf")
list
rcount <- rmultinom(n=1000, size=ss, prob=probs)
p.stats <- apply(X=rcount, MARGIN=2, FUN=pearson)
hist(x=p.stats, breaks=c(0:65)/2, freq=FALSE, main=paste0("Histogram of Pearson Stats for Simulated Data"))
curve(expr=dchisq(x=x, df=3), add=TRUE, col="red")
abline(v=qchisq(0.95, df=3), col="blue")
return(data.frame(list))

}
```

_For sample size 20_
```{r,warning=FALSE}
set.seed(123)
draw(20)
```
Chi-square curve fits the histogram not so well, but better than sample size 10. There is still a considerable amount of statistics that fall out of critical value

_For sample size 40_
```{r, warning=FALSE}
set.seed(123)
draw(40)
```
The curve fits the histogram obviously better than sample size 20. We can see less statistics fall beyond the critical value.

_For sample size 80_
```{r, warning=FALSE}
set.seed(123)
draw(80)
```
The curve fits the histogram mostly well. It is hard to see but fewer statistics are greater than critical value comparing to last one.